---
output: html_document
editor_options: 
  chunk_output_type: console
---
# This is free, open-source software under the (lenient) GNU GPLv3. It comes with no warranty. 
# Written by Dae Woong Ham between May. 2018 and August 2018. Some quality control by Rainer (Ray) K. Sachs (rks) May-August 2017.
# Script concerns synergy analysis and parsimonious modeling of WGE simple chromosome aberrations (CA) induced in 82-6 fibroblast cells by simulated GCR (Galactic Cosmic Radiation) mixed fields.
#The script uses various mixture component one-ion DERs (Dose Effect Relations), summarized in "16Cacao" = 
# = Cacao, Hada, Saganti, George and Cucinotta. "Relative Biological Effectiveness of HZE Particles for Chromosomal Exchanges and Other Surrogate Cancer Risk Endpoints." PLoS One 11(4): e0153998. (2016)].

#The libraries needed for this script
```{r}
library(ggplot2) #library for plotting
library(deSolve) # library for solving differential equations
library(gridExtra) #for plotting
library(minpack.lm) #for non-linear regression package
```

#The Data
##16Cacao Data
```{r}
#Create dataframes that store the data summarized in [Cacao E, M Hada, PB Saganti, KA George and FA Cucinotta. "Relative Biological Effectiveness of HZE Particles for Chromosomal Exchanges and Other Surrogate Cancer Risk Endpoints." PLoS One 11(4): e0153998. (2016)], "16Cacao" for short. 

Oxygen = data.frame(d = c(0, .0125, .02, .025, .05, .075, .1, .2, .4), 
                    CA = c(.24, 1.66, 2.43, 2.37, 1.16, 2.85, 2.58, 6.94, 6.91))

Si = data.frame(d = c(0, .02, .04, .06, .08, .1, .12, .2, .4, .8, 1.2), 
                    CA = c(.11, 1.26, 1.14, 1.58, 1.22, 1.89, 3.47, 4.6, 9.79, 27.01, 38.84))

Fe600 = data.frame(d = c(0, .01, .02, .04, .06, .08, .1, .12, .2, .4, .8), 
                     CA = c(.13, .76, .99, 1.2, 1.74, 1.28, 1.2, 1.7, 3.02, 5.52, 12.42))

Fe450 = data.frame(d = c(0, .02, .04, .06, .08, .1, .2, .4), 
                   CA = c(0, .86, .6, .8, 1.22, 2.02, 2.3, 4.77))

Fe300 = data.frame(d = c(0, .005, .01,  0.02, .04, .07, .1, .2, .4, .8), 
                   CA = c(0.41, 1.23, 1.47, 1.22, .97, 1.46, 1.21, 4.38, 6.22, 13.6))

Ti = data.frame(d = c(0,  0.02, .04, .06, .08, .1, .15, .3, .6), 
                   CA = c(0, 1.99, 1.88, 1.44, 2.67, 2.57, 2.50, 5.64, 11.19))

param = data.frame(ion = c("O", "Si", "Ti", "Fe600", "Fe450", "Fe300"),
                   Z = c(8, 14, 22, 26, 26, 26), L = c(75, 100, 125, 175, 195, 240), 
                   Z.beta = c(595, 690, 770, 1075, 1245, 1585))

#putting it in one big data frame
big_df = rbind(Oxygen, Si, Ti, Fe600, Fe450, Fe300)
big_df$Z = rep(param$Z, times = c(9, 11, 9, 11, 8, 10))
big_df$Z.beta = rep(param$Z.beta, times = c(9, 11, 9, 11, 8, 10))
big_df$L = rep(param$L, times = c(9, 11, 9, 11, 8, 10))
big_df$error = c(0.24, 0.63, 0.77, 0.75, 0.52, 0.82, 0.78, 1.31, 1.59, 0.12, 0.05, 0.07, 0.56, 0.18, 0.60, 1.23, 1.60, 1.55, 4.27, 7.21, 0, 0.70, 0.66, 0.59, 0.80, 0.78, 0.48, 1.15, 2.39, 0.16, 0.38, 0.24, 0.21, 0.4, 0.37, 0.54, 0.17, 0.55, 1.75, 2.59, 0, 0.43, 0.34, 0.40, 0.50, 0.64, 0.73, 1.09, 0.29, 0.55, 0.60, 0.55, 0.49, 0.60, 0.54, 1.03, 1.22, 3.62)

big_df$ion = rep(param$ion, times = c(9, 11, 9, 11, 8, 10))

#will modify the data frame to get rid of the zero dose points irrelevant to our main parameter estimation
modified_df = big_df[big_df$d != 0, ]
modified_df$CA = modified_df$CA*0.01
modified_df$error = modified_df$error*0.01
big_df$CA = big_df$CA * 0.01
big_df$error = big_df$error * 0.01
big_df$errorbar_lower = big_df$CA - big_df$error
big_df$errorbar_upper = big_df$CA + big_df$error
```

#Our Original 4 Parameter Model: Section 2.3
```{r}
original_IDER = function(d, L, Z.beta, eta0, eta1, sig0, kap) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  eta = eta0*L*exp(-eta1*L)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))
} 

#nls method to get the parameters needed (4 parameter estimation)
model_original = nls(CA ~ original_IDER(d, L, Z.beta, eta0, eta1, sig0, kap), data = modified_df, start = list(eta0 = 0.001, eta1 = 0.01, sig0 = 5, kap = 500), 
weights = (1/(modified_df$error)^2))
summary(model_original, cor = TRUE)
```

#Introducting Parsimonious Models: Section 3.1-3.4
```{r}
#3 parameter model no kap
three_IDER_no_kap = function(d, L, eta0, eta1, sig0) {
   eta = eta0*L*exp(-eta1*L)
   0.00071 + sig0*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))
}
model_three_no_kap = nls(CA ~ three_IDER_no_kap(d, L, eta0, eta1, sig0), data = modified_df, start = list(eta0 = 0.0001, eta1 = 0.01, sig0 = 1), weights = (1/(modified_df$error))^2)

#3 parameter model no eta1
three_IDER_no_eta1 = function(d, L, Z.beta, eta0, sig0, kap) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
} 
model_three_no_eta1 = nls(CA ~ three_IDER_no_eta1(d, L, Z.beta, eta0, sig0, kap), data = modified_df, start = list(eta0 = 0.001, sig0 = 1, kap = 500), weights = (1/(modified_df$error))^2)

#The 2 parameter IDER with no eta1 and no kap
two_IDER = function(d, L, eta0, sig0) {
   0.00071 + sig0*6.24*d/L*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}
model_two = nls(CA ~ two_IDER(d, L, eta0, sig0), data = modified_df, start = list(eta0 = 0.05, sig0 = 1), weights = (1/(modified_df$error))^2)

#The 2 parameter IDER with no etas at all
TE_IDER = function(d, L, kap, sig0, Z.beta) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L))
}
model_TE = nls(CA ~ TE_IDER(d, L, kap, sig0, Z.beta), data = modified_df, start = list(kap = 500, sig0 = 1), weights = (1/(modified_df$error))^2)

#The 2 parameter IDER with no etas at all
TE_one_IDER = function(d, L, sig0) {
  0.00071 + sig0*6.24*d/L*(1-exp(-1024*d/L))
}
model_one_TE = nls(CA ~ TE_one_IDER(d, L, sig0), data = modified_df, start = list(sig0 = 1), weights = (1/(modified_df$error))^2)
```

#All the models with fitted parameters: Section 3.1-3.4
```{r}
original_IDER = function(d, L, Z.beta, eta0 = coef(model_original)[1], eta1 = coef(model_original)[2], sig0 = coef(model_original)[3], kap = coef(model_original)[4]) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  eta = eta0*L*exp(-eta1*L)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))
} 

three_IDER_no_kap = function(d, L, eta0 = coef(model_three_no_kap)[1], eta1 = coef(model_three_no_kap)[2], sig0 = coef(model_three_no_kap)[3]) {
   eta = eta0*L*exp(-eta1*L)
   0.00071 + sig0*6.24*d/L*(1-exp(-1024*d/L)) + eta*(1-exp(-10^5*d))
}

three_IDER_no_eta1 = function(d, L, Z.beta, eta0 = coef(model_three_no_eta1)[1], sig0 = coef(model_three_no_eta1)[2], kap = coef(model_three_no_eta1)[3]) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
} 

two_IDER = function(d, L, eta0 = coef(model_two)[1], sig0 = coef(model_two)[2]) {
   0.00071 + sig0*6.24*d/L*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

TE_IDER = function(d, L, kap = coef(model_TE)[1], sig0 = coef(model_TE)[2], Z.beta) {
  P = (1-exp(-Z.beta/kap))^2
  sig = sig0*P + 0.041/6.24*L*(1-P)
  0.00071 + sig*6.24*d/L*(1-exp(-1024*d/L))
}

TE_one_IDER = function(d, L, sig0 = coef(model_one_TE)[1]) {
  0.00071 + sig0*6.24*d/L*(1-exp(-1024*d/L))
}

```

#Creating doses
```{r}
d_oxygen = seq(0, 0.4, 0.001)
d_si = seq(0, 1.2, 0.001)
d_ti = seq(0, 0.6, 0.001)
d_fe600 = seq(0, 0.8, 0.001)
d_fe450 = seq(0, 0.4, 0.001)
d_fe300 = seq(0, 0.8, 0.001)
```

#Parameter correlation comparison: Tables 3.1.1-3.4.1
```{r}
#Original model
cov2cor(vcov(model_original))

#3 parameter without kap
cov2cor(vcov(model_three_no_kap))

#3 parmater without eta1
cov2cor(vcov(model_three_no_eta1))

#2 parameter without kap and eta1
cov2cor(vcov(model_two))

#2 parameter without NTE
cov2cor(vcov(model_TE))
```

#Summary of fits: Tables 3.1.1-3.4.1
```{r}
summary(model_original)
summary(model_three_no_kap)
summary(model_three_no_eta1)
summary(model_two)
summary(model_TE)
```

#Figure 1: Sample Data Showing Concavity: Section 2.3
```{r}
d1 = seq(0, 1e-06, length.out = 50)
d2 = seq(1e-05, 1e-04, length.out = 30)
d3 = seq(1e-04, 1e-03, length.out = 20)
d4 = seq(1e-03, 1e-02, length.out = 20)
d5 = seq(1e-02, 4e-01, length.out = 30)

d= c(d1, d2, d3, d4, d5, 4e-05)
d = sort(d)
normal = ggplot() + geom_errorbar(data = big_df[2:9, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0)  + geom_point(aes(x = modified_df$d[1:8], y = 100*modified_df$CA[1:8]), size = 3) + geom_line(aes(x = d,  y = 100*(IDER(d = d, L = 75, Z.beta = 595))), col = "black") + labs(x = "Dose (Gy)", y = "Prevalence (%)")  + annotate("text",x = 0.025, y = 6, label = "atop(bold('A'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + xlim(c(0, 0.2)) 

d1 = seq(0, 4e-05, length.out = 500)
zoomed = c("Zoomed in Along", "Horizontal Axis 5,000x")
zoomed_very_in = ggplot() + geom_line(aes(x = d1,  y = 100*(IDER(d = d1, L = 75, Z.beta = 595))), col = "black") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "")  + ylim(0, 1.1)  + annotate("text",x = 0.5e-05, y = 0.75, label = "atop(bold('B'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + annotate("text",x = 2.5e-05, y = c(0.25, 0.15), label = zoomed, size = 6) + scale_x_continuous(breaks = c(0, 2e-5, 4e-5), limits = c(0, 4e-5))

a = ggplotGrob(normal)
b = ggplotGrob(zoomed_very_in)

b$heights = a$heights
b$widths = a$widths

pdf("concavity_IDERs.pdf", width = 10, height = 6)
grid.arrange(a,b, nrow = 1)
dev.off()


ggsave("concavity_IDERs.pdf", arrangeGrob(normal, zoomed_very_in, nrow = 1), width = 10, height = 6)
```

#Figure 2: Model Comparison Zoomed Out: Section 3.4
```{r}
oxygen_comp = ggplot() + geom_line(aes(x = d_oxygen, y = 100*original_IDER(d = d_oxygen, L = 75, Z.beta= 595)), col = "red") + geom_line(aes(x = d_oxygen, y = 100*two_IDER(d = d_oxygen, L = 75)), col = "blue") + geom_line(aes(x = d_oxygen, y = 100*three_IDER_no_eta1(d = d_oxygen, L = 75, Z.beta = 595)), col = "orange") + geom_line(aes(x = d_oxygen, y = 100*three_IDER_no_kap(d = d_oxygen, L = 75)), col = "green")  + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Oxygen") + geom_errorbar(data = big_df[big_df[, 7] == "O", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "O", ][-1, ], aes(x = d, y = 100*CA), size = 2) + geom_line(aes(x = d_oxygen, y = 100*TE_IDER(d = d_oxygen, L = 75, Z.beta = 595)), col = "purple") + theme(axis.text=element_text(size=10))  + annotate("text",x = 0.05, y = 11, label = "atop(bold('A'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), axis.title.y = element_text(vjust = 7), plot.title =element_text(size=22) ,plot.margin = margin(10, 10, 10, 20))

si_comp = ggplot() + geom_line(aes(x = d_si, y = 100*original_IDER(d = d_si, L = 100, Z.beta= 690)), col = "red") + geom_line(aes(x = d_si, y = 100*two_IDER(d = d_si, L = 100)), col = "blue") + geom_line(aes(x = d_si, y = 100*three_IDER_no_eta1(d = d_si, L = 100, Z.beta = 690)), col = "orange") + geom_line(aes(x = d_si, y = 100*three_IDER_no_kap(d = d_si, L = 100)), col = "green") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Silicon") + geom_errorbar(data = big_df[big_df[, 7] == "Si", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Si", ][-1, ], aes(x = d, y =100* CA), size = 2) + geom_line(aes(x = d_si, y = 100*TE_IDER(d = d_si, L = 100, Z.beta = 690)), col = "purple") + annotate("text",x = 0.13, y = 33, label = "atop(bold('B'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.5, 1.00))

ti_comp = ggplot() + geom_line(aes(x = d_ti, y = 100*original_IDER(d = d_ti, L = 125, Z.beta= 770)), col = "red") + geom_line(aes(x = d_ti, y = 100*two_IDER(d = d_ti, L = 125)), col = "blue")+ geom_line(aes(x = d_ti, y = 100*three_IDER_no_eta1(d = d_ti, L = 125, Z.beta = 770)), col = "orange") + geom_line(aes(x = d_ti, y = 100*three_IDER_no_kap(d = d_ti, L = 125)), col = "green") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Titanium") + geom_errorbar(data = big_df[big_df[, 7] == "Ti", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Ti", ][-1, ], aes(x = d, y = 100*CA), size = 2) + geom_line(aes(x = d_ti, y = 100*TE_IDER(d = d_ti, L = 125, Z.beta = 770)), col = "purple")+ theme(axis.text=element_text(size=10)) + annotate("text",x = 0.08, y = 12., label = "atop(bold('C'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

fe300_comp = ggplot() + geom_line(aes(x = d_fe300, y = 100*original_IDER(d = d_fe300, L = 175, Z.beta= 1075)), col = "red") + geom_line(aes(x = d_fe300, y = 100*two_IDER(d = d_fe300, L = 175)), col = "blue") + geom_line(aes(x = d_fe300, y = 100*three_IDER_no_eta1(d = d_fe300, L = 175, Z.beta = 1075)), col = "orange") + geom_line(aes(x = d_fe300, y = 100*three_IDER_no_kap(d = d_fe300, L = 175)), col = "green")+ labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.65") + geom_errorbar(data = big_df[big_df[, 7] == "Fe300", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe300", ][-1, ], aes(x = d, y = 100*CA), size = 2) + geom_line(aes(x = d_fe300, y = 100*TE_IDER(d = d_fe300, L = 175, Z.beta = 1075)), col = "purple") + annotate("text",x = 0.1, y = 12, label = "atop(bold('D'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), axis.title.y = element_text(vjust = 7), plot.title =element_text(size=22) ,plot.margin = margin(10, 10, 10, 20))

fe450_comp = ggplot() + geom_line(aes(x = d_fe450, y = 100*original_IDER(d = d_fe450, L = 195, Z.beta= 1245)), col = "red") + geom_line(aes(x = d_fe450, y = 100*two_IDER(d = d_fe450, L = 195)), col = "blue") + geom_line(aes(x = d_fe450, y = 100*three_IDER_no_eta1(d = d_fe450, L = 195, Z.beta = 1245)), col = "orange") + geom_line(aes(x = d_fe450, y = 100*three_IDER_no_kap(d = d_fe450, L = 195)), col = "green")+  labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.74") + geom_errorbar(data = big_df[big_df[, 7] == "Fe450", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe450", ][-1, ], aes(x = d, y = 100*CA), size = 2) + geom_line(aes(x = d_fe450, y = 100*TE_IDER(d = d_fe450, L = 195, Z.beta = 1245)), col = "purple") + annotate("text",x = 0.05, y = 5, label = "atop(bold('E'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

fe600_comp = ggplot() + geom_line(aes(x = d_fe600, y = 100*original_IDER(d = d_fe600, L = 240, Z.beta= 1585)), col = "red") + geom_line(aes(x = d_fe600, y = 100*two_IDER(d = d_fe600, L = 240)), col = "blue")+ labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.79") + geom_line(aes(x = d_fe600, y = 100*three_IDER_no_eta1(d = d_fe600, L = 240, Z.beta = 1585)), col = "orange") + geom_line(aes(x = d_fe600, y = 100*three_IDER_no_kap(d = d_fe600, L = 240)), col = "green") +  geom_errorbar(data = big_df[big_df[, 7] == "Fe600", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe600", ][-1, ], aes(x = d, y = 100*CA), size = 2) + geom_line(aes(x = d_fe600, y = 100*TE_IDER(d = d_fe600, L = 240, Z.beta = 1585)), col = "purple") + annotate("text",x = 0.1, y = 10, label = "atop(bold('F'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

oxygen = ggplotGrob(oxygen_comp)
si = ggplotGrob(si_comp)
ti = ggplotGrob(ti_comp)
fe300 = ggplotGrob(fe300_comp)
fe450 = ggplotGrob(fe450_comp)
fe600 = ggplotGrob(fe600_comp)

si$heights = oxygen$heights
si$widths = oxygen$widths

ti$heights = oxygen$heights
ti$widths = oxygen$widths

fe450$heights = fe300$heights
fe450$widths = fe300$widths

fe600$heights = fe450$heights
fe600$widths = fe450$widths

pdf("IDER_fig_zoomedout.pdf", width = 9, height = 7)
grid.arrange(oxygen, si, ti, fe300, fe450, fe600, ncol = 3)
dev.off()

```

#Figure 3: Model Comparison Zoomed Very In: Section 3.4
```{r}
oxygen_comp = ggplot() + geom_line(aes(x = d_oxygen, y = 100*original_IDER(d = d_oxygen, L = 75, Z.beta= 595)), col = "red") + geom_line(aes(x = d_oxygen, y = 100*two_IDER(d = d_oxygen, L = 75)), col = "blue") + geom_line(aes(x = d_oxygen, y = 100*three_IDER_no_eta1(d = d_oxygen, L = 75, Z.beta = 595)), col = "orange") + geom_line(aes(x = d_oxygen, y = 100*three_IDER_no_kap(d = d_oxygen, L = 75)), col = "green")  + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Oxygen") + geom_errorbar(data = big_df[big_df[, 7] == "O", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "O", ][-1, ], aes(x = d, y = 100*CA), size = 3) + geom_line(aes(x = d_oxygen, y = 100*TE_IDER(d = d_oxygen, L = 75, Z.beta = 595)), col = "purple") + theme(axis.text=element_text(size=10))  + annotate("text",x = 0.01, y = 3.2, label = "atop(bold('A'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), axis.title.y = element_text(vjust = 7), plot.title =element_text(size=22) ,plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.05, 0.1), limits = c(0, 0.1)) + ylim(0, 4) 

si_comp = ggplot() + geom_line(aes(x = d_si, y = 100*original_IDER(d = d_si, L = 100, Z.beta= 690)), col = "red") + geom_line(aes(x = d_si, y = 100*two_IDER(d = d_si, L = 100)), col = "blue") + geom_line(aes(x = d_si, y = 100*three_IDER_no_eta1(d = d_si, L = 100, Z.beta = 690)), col = "orange") + geom_line(aes(x = d_si, y = 100*three_IDER_no_kap(d = d_si, L = 100)), col = "green") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Silicon") + geom_errorbar(data = big_df[big_df[, 7] == "Si", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Si", ][-1, ], aes(x = d, y =100* CA), size = 3) + geom_line(aes(x = d_si, y = 100*TE_IDER(d = d_si, L = 100, Z.beta = 690)), col = "purple") + annotate("text",x = 0.012, y = 1.9, label = "atop(bold('B'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.05, 0.1), limits = c(0, 0.1))+ ylim(0, 2.5)

ti_comp = ggplot() + geom_line(aes(x = d_ti, y = 100*original_IDER(d = d_ti, L = 125, Z.beta= 770)), col = "red") + geom_line(aes(x = d_ti, y = 100*two_IDER(d = d_ti, L = 125)), col = "blue")+ geom_line(aes(x = d_ti, y = 100*three_IDER_no_eta1(d = d_ti, L = 125, Z.beta = 770)), col = "orange") + geom_line(aes(x = d_ti, y = 100*three_IDER_no_kap(d = d_ti, L = 125)), col = "green") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Titanium") + geom_errorbar(data = big_df[big_df[, 7] == "Ti", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Ti", ][-1, ], aes(x = d, y = 100*CA), size = 3) + geom_line(aes(x = d_ti, y = 100*TE_IDER(d = d_ti, L = 125, Z.beta = 770)), col = "purple")+ theme(axis.text=element_text(size=10)) + annotate("text",x = 0.013, y = 3.1, label = "atop(bold('C'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.05, 0.1), limits = c(0, 0.1)) + ylim(0, 4) 

fe300_comp = ggplot() + geom_line(aes(x = d_fe300, y = 100*original_IDER(d = d_fe300, L = 175, Z.beta= 1075)), col = "red") + geom_line(aes(x = d_fe300, y = 100*two_IDER(d = d_fe300, L = 175)), col = "blue") + geom_line(aes(x = d_fe300, y = 100*three_IDER_no_eta1(d = d_fe300, L = 175, Z.beta = 1075)), col = "orange") + geom_line(aes(x = d_fe300, y = 100*three_IDER_no_kap(d = d_fe300, L = 175)), col = "green")+ labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.65") + geom_errorbar(data = big_df[big_df[, 7] == "Fe300", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe300", ][-1, ], aes(x = d, y = 100*CA), size = 3) + geom_line(aes(x = d_fe300, y = 100*TE_IDER(d = d_fe300, L = 175, Z.beta = 1075)), col = "purple") + annotate("text",x = 0.013, y = 2.3, label = "atop(bold('D'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), axis.title.y = element_text(vjust = 7), plot.title =element_text(size=22) ,plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.05, 0.1), limits = c(0, 0.1)) + ylim(0, 3)

fe450_comp = ggplot() + geom_line(aes(x = d_fe450, y = 100*original_IDER(d = d_fe450, L = 195, Z.beta= 1245)), col = "red") + geom_line(aes(x = d_fe450, y = 100*two_IDER(d = d_fe450, L = 195)), col = "blue") + geom_line(aes(x = d_fe450, y = 100*three_IDER_no_eta1(d = d_fe450, L = 195, Z.beta = 1245)), col = "orange") + geom_line(aes(x = d_fe450, y = 100*three_IDER_no_kap(d = d_fe450, L = 195)), col = "green")+  labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.74") + geom_errorbar(data = big_df[big_df[, 7] == "Fe450", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe450", ][-1, ], aes(x = d, y = 100*CA), size = 3) + geom_line(aes(x = d_fe450, y = 100*TE_IDER(d = d_fe450, L = 195, Z.beta = 1245)), col = "purple")+ theme(axis.text=element_text(size=10)) + annotate("text",x = 0.013, y = 2.3, label = "atop(bold('E'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.05, 0.1), limits = c(0, 0.1)) + ylim(0, 3) 

fe600_comp = ggplot() + geom_line(aes(x = d_fe600, y = 100*original_IDER(d = d_fe600, L = 240, Z.beta= 1585)), col = "red") + geom_line(aes(x = d_fe600, y = 100*two_IDER(d = d_fe600, L = 240)), col = "blue")+ labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.79") + geom_line(aes(x = d_fe600, y = 100*three_IDER_no_eta1(d = d_fe600, L = 240, Z.beta = 1585)), col = "orange") + geom_line(aes(x = d_fe600, y = 100*three_IDER_no_kap(d = d_fe600, L = 240)), col = "green") +  geom_errorbar(data = big_df[big_df[, 7] == "Fe600", ][-1, ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe600", ][-1, ], aes(x = d, y = 100*CA), size = 3) + geom_line(aes(x = d_fe600, y = 100*TE_IDER(d = d_fe600, L = 240, Z.beta = 1585)), col = "purple") + annotate("text",x = 0.012, y = 1.9, label = "atop(bold('F'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20)) + scale_x_continuous(breaks = c(0, 0.05, 0.1), limits = c(0, 0.1)) + ylim(0, 2.5) 

oxygen = ggplotGrob(oxygen_comp)
si = ggplotGrob(si_comp)
ti = ggplotGrob(ti_comp)
fe300 = ggplotGrob(fe300_comp)
fe450 = ggplotGrob(fe450_comp)
fe600 = ggplotGrob(fe600_comp)

si$heights = oxygen$heights
si$widths = oxygen$widths

ti$heights = oxygen$heights
ti$widths = oxygen$widths

fe450$heights = fe300$heights
fe450$widths = fe300$widths

fe600$heights = fe450$heights
fe600$widths = fe450$widths

pdf("IDER_fig_zoomedinx2.pdf", width = 9, height = 7)
grid.arrange(oxygen_comp, si_comp, ti_comp, fe300_comp, fe450_comp, fe600_comp, ncol = 3)
dev.off()

```

#Table 4.1.1: Model Selection - AIC/BIC
```{r}
original_AIC = AIC(model_original); original_BIC = BIC(model_original)

three_no_kap_AIC = AIC(model_three_no_kap); three_no_kap_BIC = BIC(model_three_no_kap)

three_no_eta1_AIC = AIC(model_three_no_eta1); three_no_eta1_BIC = BIC(model_three_no_eta1)

two_AIC = AIC(model_two); two_BIC = BIC(model_two)

TE_AIC = AIC(model_TE); TE_BIC = BIC(model_TE)

matrix(c(original_AIC, three_no_kap_AIC, three_no_eta1_AIC, two_AIC, TE_AIC ,original_BIC, three_no_kap_BIC, three_no_eta1_BIC, two_BIC, TE_BIC), nrow = 5, dimnames = list(c("Original 4 Parameter", "3 Parameter no Kap", "Three Parameter no eta1", "Two Parameter", "TE Only"), c("AIC", "BIC")))
```

#Table 4.1.1: Cross Validation - 6 fold
```{r}
#Measure of fit is using Median absolute deviation known. 

ion = unique(modified_df$ion)
#CV for 3 parameter no kap
cv_error_three_no_kap <- function(data = modified_df) {
  theoretical = vector()
  observed = vector()
  for (i in 1:6) {
    train_data = modified_df[!modified_df$ion == ion[i], ]
    test_data = modified_df[modified_df$ion == ion[i], ]
    fit = nls(CA ~ three_IDER_no_kap(d, L, eta0, eta1, sig0), data = train_data, start = list(eta0 = 0.0001, eta1 = 0.01, sig0 = 1), weights = (1/(train_data$error))^2)
    predic = predict(fit, test_data)
    actual = test_data$CA
    theoretical = c(theoretical, predic)
    observed = c(observed, actual)
  }
  error = median(abs(theoretical - observed))
  return(error)
}

cv_errors_three_no_kap = cv_error_three_no_kap()

#CV for 3 parameter no eta1
cv_error_three_no_eta1 <- function(data = modified_df) {
  theoretical = vector()
  observed = vector()
  for (i in 1:5) {
    train_data = modified_df[!modified_df$ion == ion[i], ]
    test_data = modified_df[modified_df$ion == ion[i], ]
    fit = nls(CA ~ three_IDER_no_eta1(d, L, Z.beta, eta0, sig0, kap), data = train_data, start = list(eta0 = 0.001, sig0 = 1, kap = 500), weights = (1/(train_data$error))^2)
    predic = predict(fit, test_data)
    actual = test_data$CA
    theoretical = c(theoretical, predic)
    observed = c(observed, actual)
  }
  error = median(abs(theoretical - observed))
  return(error)
}

cv_errors_three_no_eta1 = cv_error_three_no_eta1()

#Cross validation for two parameter
cv_error_two <- function(data = modified_df) {
  theoretical = vector()
  observed = vector()
  for (i in 1:6) {
    train_data = modified_df[!modified_df$ion == ion[i], ]
    test_data = modified_df[modified_df$ion == ion[i], ]
    fit = nls(CA ~ two_IDER(d, L, eta0, sig0), data = train_data, start = list(eta0 = 0.05, sig0 = 1), weights = (1/(train_data$error))^2)
    predic = predict(fit, test_data)
    actual = test_data$CA
    theoretical = c(theoretical, predic)
    observed = c(observed, actual)
  }
  error = median(abs(theoretical - observed))
  return(error)
}

cv_errors_two = cv_error_two()

#Cross validation for TE model
cv_error_TE <- function(data = modified_df) {
  sum_error = vector(length = 5)
  theoretical = vector()
  observed = vector()
  for (i in 2:6) {
    train_data = modified_df[!modified_df$ion == ion[i], ]
    test_data = modified_df[modified_df$ion == ion[i], ]
    fit = nls(CA ~ TE_IDER(d, L, kap, sig0 ,Z.beta), data = train_data, start = list(kap = 500, sig0 = 1), weights = (1/(train_data$error))^2)
    predic = predict(fit, test_data)
    actual = test_data$CA
    theoretical = c(theoretical, predic)
    observed = c(observed, actual)
  }
  error = median(abs(theoretical - observed))
  return(error)
}

cv_errors_TE = cv_error_TE()

#Cross validation for original model
cv_error_originalmodel <- function(data = modified_df) {
  theoretical = vector()
  observed = vector()
  for (i in 1:6) {
    train_data = modified_df[!modified_df$ion == ion[i], ]
    test_data = modified_df[modified_df$ion == ion[i], ]
    fit = nls(CA ~ original_IDER(d, L, Z.beta, eta0, eta1, sig0, kap), data = modified_df, start = list(eta0 = 0.001, eta1 = 0.01, sig0 = 5, kap = 500), weights = (1/(modified_df$error)^2))
    predic = predict(fit, test_data)
    actual = test_data$CA
    theoretical = c(theoretical, predic)
    observed = c(observed, actual)
  }
  error = median(abs(theoretical - observed))
  return(error)
}
cv_errors_original = cv_error_originalmodel()


matrix(c(cv_errors_three_no_eta1, cv_errors_three_no_kap, cv_errors_two, cv_errors_TE ,cv_errors_original), nrow = 1, dimnames = list(c("CV Error"), c("Three Parameters No Eta1", "Three Parameters No Kap", "Two Parameters", "TE Model","Original Four Parameters")))
```

##Expansion Modelling Supplementary Section 2
#Oxygen Individual Fit
```{r}
IDER_oxygen = function(d, L, eta0, sig0) {
  0.0024 + sig0*d*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

oxygen_df = big_df[1:9, ]
oxygen_df_w0 = oxygen_df[-1, ]
oxygen_model = nls(CA ~ IDER_oxygen(d, L, eta0, sig0), data = oxygen_df_w0, start = list(eta0 = 0.01, sig0 = 1), 
weights = (1/(oxygen_df_w0$error)^2))
summary(oxygen_model)
```

#Si Individaul Fit
```{r}
si_df = big_df[big_df[, 7] == "Si", ]
si_df_w0 = si_df[-1, ]
si_df[1, 2] #0.0011 is the intercept
IDER_si= function(d, L, eta0, sig0) {
  0.0011 + sig0*d*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

si_model = nls(CA ~ IDER_si(d, L, eta0, sig0), data = si_df_w0, start = list(eta0 = 0.01, sig0 = 1), 
weights = (1/(si_df_w0$error)^2))
summary(si_model)
```

#Ti individual fit
```{r}
ti_df = big_df[big_df[, 7] == "Ti", ]
ti_df_w0 = ti_df[-1, ]
ti_df[1, 2] #0.0011 is the intercept
IDER_ti= function(d, L, eta0, sig0) {
  sig0*d*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

ti_model = nls(CA ~ IDER_ti(d, L, eta0, sig0), data = ti_df_w0, start = list(eta0 = 0.01, sig0 = 1), 
weights = (1/(ti_df_w0$error)^2))
summary(ti_model)
```

#Fe_600 individual fit
```{r}
fe600_df = big_df[big_df[, 7] == "Fe600", ]
fe600_df_w0 = fe600_df[-1, ]
fe600_df[1, 2] #0.0013 is the intercept
IDER_fe600= function(d, L, eta0, sig0) {
  0.0013 + sig0*d*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

fe600_model = nls(CA ~ IDER_fe600(d, L, eta0, sig0), data = fe600_df_w0, start = list(eta0 = 0.01, sig0 = 1), 
weights = (1/(fe600_df_w0$error)^2))
```

#Fe_450 individual fit
```{r}
fe450_df = big_df[big_df[, 7] == "Fe450", ]
fe450_df_w0 = fe450_df[-1, ]
fe450_df[1, 2] 
IDER_fe450= function(d, L, eta0, sig0) {
  sig0*d*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

fe450_model = nls(CA ~ IDER_fe450(d, L, eta0, sig0), data = fe450_df_w0, start = list(eta0 = 0.01, sig0 = 1), 
weights = (1/(fe450_df_w0$error)^2))
summary(fe450_model)

```

#Fe_300 individual fit
```{r}
fe300_df = big_df[big_df[, 7] == "Fe300", ]
fe300_df_w0 = fe300_df[-1, ]
fe300_df[1, 2] 
IDER_fe300= function(d, L, eta0, sig0) {
  0.0041 + sig0*d*(1-exp(-1024*d/L)) + eta0*(1-exp(-10^5*d))
}

fe300_model = nls(CA ~ IDER_fe300(d, L, eta0, sig0), data = fe300_df_w0, start = list(eta0 = 0.01, sig0 = 1), 
weights = (1/(fe300_df_w0$error)^2))
summary(fe300_model)

```

#Graphing individual ion fit 
```{r}
#Just 2 parameter and 4 parameter comparison
oxygen_comp = ggplot() + geom_line(aes(x = d_oxygen, y = 100*original_IDER(d = d_oxygen, L = 75, Z.beta= 595)), col = "red") + geom_line(aes(x = d_oxygen, y = 100*two_IDER(d = d_oxygen, L = 75)), col = "blue") + geom_line(aes(x = d_oxygen, y = 100*IDER_oxygen(d = d_oxygen, eta0 = coef(oxygen_model)[1], sig0 = coef(oxygen_model)[2],L = 75)), col = "orange") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Oxygen") + geom_errorbar(data = big_df[big_df[, 7] == "O", ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "O", ], aes(x = d, y = 100*CA), size = 2) + annotate("text",x = 0.05, y = 8.5, label = "atop(bold('A'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

si_comp = ggplot() + geom_line(aes(x = d_si, y = 100*original_IDER(d = d_si, L = 100, Z.beta= 690)), col = "red") + geom_line(aes(x = d_si, y = 100*two_IDER(d = d_si, L = 100)), col = "blue") + geom_line(aes(x = d_si, y = 100*IDER_si(d = d_si, eta0 = coef(si_model)[1], sig0 = coef(si_model)[2],L = 100)), col = "orange") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Silicon") + geom_errorbar(data = big_df[big_df[, 7] == "Si", ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Si", ], aes(x = d, y = 100*CA), size = 2) + xlim(c(0, 0.4)) + ylim(c(0, 12.5)) + annotate("text",x = 0.05, y = 9, label = "atop(bold('B'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

ti_comp = ggplot() + geom_line(aes(x = d_ti, y = 100*original_IDER(d = d_ti, L = 125, Z.beta= 770)), col = "red") + geom_line(aes(x = d_ti, y = 100*two_IDER(d = d_ti, L = 125)), col = "blue")+ geom_line(aes(x = d_ti, y = 100*IDER_ti(d = d_ti, eta0 = coef(ti_model)[1], sig0 = coef(ti_model)[2],L = 125)), col = "orange") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Titanium") + geom_errorbar(data = big_df[big_df[, 7] == "Ti", ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Ti", ], aes(x = d, y = 100*CA), size = 2) + xlim(c(0, 0.4)) + ylim(c(0, 7.5)) + annotate("text",x = 0.05, y = 5.5, label = "atop(bold('C'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

fe300_comp = ggplot() + geom_line(aes(x = d_fe300, y = 100*original_IDER(d = d_fe300, L = 175, Z.beta= 1075)), col = "red") + geom_line(aes(x = d_fe300, y = 100*two_IDER(d = d_fe300, L = 175)), col = "blue") + geom_line(aes(x = d_fe300, y = 100*IDER_fe300(d = d_fe300, eta0 = coef(fe300_model)[1], sig0 = coef(fe300_model)[2],L = 175)), col = "orange") + labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.65") + geom_errorbar(data = big_df[big_df[, 7] == "Fe300", ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe300", ], aes(x = d, y = 100*CA), size = 2) + xlim(c(0, 0.4)) + ylim(c(0, 7.5)) + annotate("text",x = 0.05, y = 5.5, label = "atop(bold('D'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

fe450_comp = ggplot() + geom_line(aes(x = d_fe450, y = 100*original_IDER(d = d_fe450, L = 195, Z.beta= 1245)), col = "red") + geom_line(aes(x = d_fe450, y = 100*two_IDER(d = d_fe450, L = 195)), col = "blue") + geom_line(aes(x = d_fe450, y = 100*IDER_fe450(d = d_fe450, eta0 = coef(fe450_model)[1], sig0 = coef(fe450_model)[2],L = 195)), col = "orange") +  labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.74") + geom_errorbar(data = big_df[big_df[, 7] == "Fe450", ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe450", ], aes(x = d, y = 100*CA), size = 2) + annotate("text",x = 0.05, y = 4.5, label = "atop(bold('E'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

fe600_comp = ggplot() + geom_line(aes(x = d_fe600, y = 100*original_IDER(d = d_fe600, L = 240, Z.beta= 1585)), col = "red") + geom_line(aes(x = d_fe600, y = 100*two_IDER(d = d_fe600, L = 240)), col = "blue")+ labs(x = "Dose (Gy)", y = "Prevalence (%)", title = "Fe0.79") + geom_line(aes(x = d_fe600, y = 100*IDER_fe600(d = d_fe600, eta0 = coef(fe600_model)[1], sig0 = coef(fe600_model)[2],L = 240)), col = "orange")  +  geom_errorbar(data = big_df[big_df[, 7] == "Fe600", ], aes(x = d, ymin = 100*errorbar_lower, ymax = 100*errorbar_upper), col = "black", width = 0) + geom_point(data = big_df[big_df[, 7] == "Fe600", ], aes(x = d, y = 100*CA), size = 2) + xlim(c(0, 0.4)) + ylim(c(0, 7.5)) + annotate("text",x = 0.05, y = 5.5, label = "atop(bold('F'))", size = 8, parse = TRUE) + theme(axis.text=element_text(size=15), axis.title=element_text(size=19), plot.title =element_text(size=22), axis.title.y = element_text(vjust = 7), plot.margin = margin(10, 10, 10, 20))

pdf("IDER_fig_expansaion.pdf", width = 9, height = 7)
grid.arrange(oxygen_comp, si_comp, ti_comp, fe300_comp, fe450_comp, fe600_comp, ncol = 3)
dev.off()
```

#CV Error for twelve parameter model
```{r}
vec = c(sum(residuals(oxygen_model)^2), sum(residuals(si_model)^2), sum(residuals(ti_model)^2), sum(residuals(fe300_model)^2), sum(residuals(fe450_model)^2), sum(residuals(fe600_model)^2))
cv_error_twelve = mean(vec)
cv_error_twelve
```

